---
title: "reproducable research project 2"
author: "Yaswanth Pulavarthi"
date: "8/3/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# US Storm data analysis

## 1 Data processing
loaded the data using read.csv function, because it can automatically extracts file and load into csv.
just took the required columns needed for analysis and set cache= TRUE.

## load data

```{r data-processing,cache=TRUE}
read.csv("C:\\Users\\Yaswanth Pulavarthi\\Downloads\\repdata_data_StormData.csv.bz2")->data
names(data)
req.col<-c("EVTYPE","FATALITIES","INJURIES","PROPDMG","PROPDMGEXP","CROPDMG","CROPDMGEXP" )
data<-data[,req.col]
head(data)
```

## damagecosts

### property damage costs
listed the types of property damage expenses using unique function
```{r uniquepropexp,}
unique(data$PROPDMGEXP)
```
changed the character variables of PROPDMGEXP  into numbers .i.e: K =1000,M=1,000,000 and 0 for invalid data(?,+,-).
And, created new colomn in data table, which gives the information about property loss
```{r propdmgcost,}
# Assigning values for the property data 
data$PROPEXP[data$PROPDMGEXP == "K" | data$PROPDMGEXP == "3"] <- 1000
data$PROPEXP[data$PROPDMGEXP == "M" | data$PROPDMGEXP == "m" | data$PROPDMGEXP == "6"] <- 1e+06
data$PROPEXP[data$PROPDMGEXP == ""] <- 1
data$PROPEXP[data$PROPDMGEXP == "B"] <- 1e+09
data$PROPEXP[data$PROPDMGEXP == "0"] <- 1
data$PROPEXP[data$PROPDMGEXP == "5"] <- 1e+05
data$PROPEXP[data$PROPDMGEXP == "4"] <- 10000
data$PROPEXP[data$PROPDMGEXP == "2" | data$PROPDMGEXP == "h" | data$PROPDMGEXP == "H"] <- 100
data$PROPEXP[data$PROPDMGEXP == "7"] <- 1e+07
data$PROPEXP[data$PROPDMGEXP == "1"] <- 10
data$PROPEXP[data$PROPDMGEXP == "8"] <- 1e+08
# Assigning '0' to invalid data
data$PROPEXP[data$PROPDMGEXP == "+" | data$PROPDMGEXP == "-" |data$PROPDMGEXP == "?"] <- 0
# Calculating the property damage value
data$PROPDMGCOST <- data$PROPDMG * data$PROPEXP

```
Similarly, like above changed the exponent data into numbers and created a new column with crop damage loss
```{r uniquecropexp,}
unique(data$CROPDMGEXP)
```

```{r cropdmgexp,}
# Assigning values for the crop exponent data 
data$CROPEXP[data$CROPDMGEXP == "M" | data$CROPDMGEXP == "m"] <- 1e+06
data$CROPEXP[data$CROPDMGEXP == "K" | data$CROPDMGEXP == "k"] <- 1000
data$CROPEXP[data$CROPDMGEXP == "B"] <- 1e+09
data$CROPEXP[data$CROPDMGEXP == "0" | data$CROPDMGEXP == ""] <- 1
data$CROPEXP[data$CROPDMGEXP == "2"] <- 100

# Assigning '0' to invalid exponent data
data$CROPEXP[data$CROPDMGEXP == "?"] <- 0
# calculating the crop damage value
data$CROPDMGCOST <- data$CROPDMG * data$CROPEXP
```
Sorted the data by event types for Fatalities, Injuries,Property Damage Costs,Crop damage Costs.
And by using sorted data, listed out top 10 events caused high loss.
```{r top10dmgs,}
 fatal <- aggregate(FATALITIES ~ EVTYPE, data, FUN = sum)
fatal10 <- fatal[order(-fatal$FATALITIES), ][1:10, ]
 injury <- aggregate(INJURIES ~ EVTYPE, data, FUN = sum)
injury10 <- injury[order(-injury$INJURIES), ][1:10, ]
 propdmg <- aggregate(PROPDMGCOST ~ EVTYPE, data, FUN = sum)
propdmg10 <- propdmg[order(-propdmg$PROPDMGCOST), ][1:10, ]
 cropdmg <- aggregate(CROPDMGCOST ~ EVTYPE, data, FUN = sum)
cropdmg10 <- cropdmg[order(-cropdmg$CROPDMGCOST), ][1:10, ]

```

ploted the top 10 events for high fatalities and high injuries
```{r plothumanloss}
 par(mfrow = c(1, 2), mar = c(12, 4, 3, 2), mgp = c(3, 1, 0), cex = 0.8)
 barplot(fatal10$FATALITIES, las = 3, names.arg = fatal10$EVTYPE, main = "Highest Fatalities by event", col = "red")
 barplot(injury10$INJURIES, las = 3, names.arg = injury10$EVTYPE, main = "Highest Injuries by event", col = "light green")
```

ploted top 10 events for high crop and property loss
```{r plotdmgloss}
par(mfrow = c(1, 2), mar = c(12, 4, 3, 2), mgp = c(3, 1, 0), cex = 0.8)
barplot(propdmg10$PROPDMGCOST, las = 3, names.arg = propdmg10$EVTYPE, main = "Top 10 property loss by event", col = "light blue")
barplot(cropdmg10$CROPDMGCOST, las = 3, names.arg = cropdmg10$EVTYPE, main = "Top 10 crop loss by event", col = "light blue")
```


# Result
As per plot-1, there are highest fatalities and injuries due to Tornado.
Highest Property damage due to Floods and highest crop damage due to Droughts




