---
title: "Iris App"
author: "Yaswanth Pulavarthi"
date: "9/19/2020"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Description
With this app we can easily do some data analysis on iris data. i.e change in sepal length of a flower with change in other variables in data.


- Prediction of Sepal Length wrt Sepal Width
- Prediction of Sepal Length wrt Petal Length
- Prediction of Sepal Length wrt Petal Width
- Prediction with best lm fit
-plotted points of Sepal length wrt to Sepal.Width,Petal.Length,and Petal.Width.
And also, for each plot added regression lines with respect to Species factor. 

## UI code

```{r cars, echo = TRUE, eval=FALSE}
library(shiny)
shinyUI(fluidPage(
    titlePanel("Iris Data"),
    sidebarLayout(
        sidebarPanel(
            sliderInput("SepalWidth", "Set Sepal Width",min = 2.0, max = 4.4,value = 3.4, step = 0.1),
            sliderInput("PetalLength", "Set Petal Length",min = 1.0, max = 6.9,value = 1.5, step = 0.1),
            sliderInput("PetalWidth", "Set Petal Width",min = 0.1, max = 2.5,value = 0.2, step = 0.1),
            selectInput("Species", "Species?",
                        c("setosa" = "setosa",
                          "versicolor" = "versicolor",
                          "virginica" = "virginica")),
             
            submitButton("Submit")
        ),
        mainPanel(
            
            tabsetPanel(type = "tabs", 
                        tabPanel("Sepal Width", br(), textOutput("out1"),plotOutput("plot1"),
                                 h3("Predicted Sepal Length wrt Sepal Width:"),
                                 textOutput("pred1")), 
                        tabPanel("Petal Width", br(), textOutput("out2"),plotOutput("plot2"),
                                 h3("Predicted Sepal Lenght wrt Petal Length:"),
                                 textOutput("pred2")), 
                        tabPanel("Petal Length", br(), textOutput("out3"),plotOutput("plot3"),
                                 h3("Predicted Sepal Length wrt Petal Width: "),
                                 textOutput("pred3"))
            ),
            h2("Best fit:"),
            h5("(Predicted Sepal Length wrt Sepal.Width+Petal.Length+Petal.Width+Species)"),
            verbatimTextOutput("finalpred"),
            tags$head(tags$style(HTML("
                            #finalpred {
                              font-size: 25px;
                            }
                            ")))
            
            
        )
    )
))
```

## Server code

```{r pressure,echo=TRUE,eval=FALSE}
(function(input, output) {
    model1 <-lm(Sepal.Length~Sepal.Width,data=iris)
    model2 <-lm(Sepal.Length~Petal.Length,data=iris)
    model3 <-lm(Sepal.Length~Petal.Width,data=iris)
    bestfit <- lm(Sepal.Length~.,data=iris)
    model1pred <- reactive({

        predict(model1, newdata = data.frame(Sepal.Width  = input$SepalWidth))
    })
    
    model2pred <- reactive({

        predict(model2, newdata = data.frame(Petal.Length  = input$PetalLength))
    })
    model3pred <- reactive({
        
        predict(model3, newdata = data.frame(Petal.Width = input$PetalWidth))
    })
    
    bestfitpred <- reactive({
        
        predict(bestfit, newdata = data.frame(Sepal.Width  = input$SepalWidth,Petal.Length  = input$PetalLength,Petal.Width = input$PetalWidth,Species=as.factor(input$Species)))
    })
    
    
    output$plot1 <- renderPlot({
        ggplot(data=iris, aes(x=Sepal.Length, y=Sepal.Width, col=Species))+geom_point()+stat_smooth(method='lm')
    })
    
    output$pred1 <- renderText({
        model1pred()
    })
    
    output$plot2 <- renderPlot({
        ggplot(data=iris, aes(x=Sepal.Length, y=Petal.Length, col=Species))+geom_point()+stat_smooth(method='lm')
    })
    output$pred2 <- renderText({
        model2pred()
    })
    output$plot3 <- renderPlot({
        ggplot(data=iris, aes(x=Sepal.Length, y=Petal.Width, col=Species))+geom_point()+stat_smooth(method='lm')
    })
    output$pred3 <- renderText({
        model3pred()
    })
    output$finalpred <- renderText({
        bestfitpred()
    })
    output$out1 <- renderText(input$box1)
    output$out2 <- renderText(input$box2)
    output$out3 <- renderText(input$box3)
})
```

