---
title: "Cars-data"
author: "Yaswanth Pulavarthi"
date: "9/14/2020"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading data


```{r cars}
library(datasets)
data(mtcars)
head(mtcars)
library(ggplot2)
```

## Processing Data



```{r dataProccess }
mtcars$cyl <- as.factor(mtcars$cyl)
mtcars$vs <- as.factor(mtcars$vs)
mtcars$am <- as.factor(mtcars$am)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb<- factor(mtcars$carb)
str(mtcars)

```


## Basic Exploratory analysis



```{r boxplot}
boxplot(mpg~am, mtcars)
```



```{r meanam}

aggregate(mpg ~ am, data = mtcars, mean)

```
## single var fit



```{r }
FitAM <- lm(mpg ~ am, data = mtcars)
summary(FitAM)

```

only 35% of variance is explained


## multi variable fit



```{r multifit }
multiVarFit <- lm(mpg ~., data = mtcars)
summary(multiVarFit)
```

```{r anova }
anova(FitAM,multiVarFit)
```
here using multivarfit we can reject the null hypothesis but their is significant change from fitam

```{r ttest}
t.test(mtcars$mpg~mtcars$am)

```

P-value less than 0.05,we reject the null hypothesis that there is no difference in MPG. This concludes that manual transmission works better than automatic.

## slope of variables with respect to mpg

```{r pairs }

pairs(mtcars)

```
## best fit

```{r bestfit}
bestfit <-step(multiVarFit,direction = "both")
summary(bestfit)

```

In this bestfit model 86.59% of variance is explained. So, we choose this model for comparision. 

## residual plot
```{r residplot }
plot(bestfit, which=1)
```


# summary 
by this, we can clearly say that manual transmission is better than  automatic. and, manual mpg is greater than automatic by 1.8 times. However, we need to consider other vaiables than transmission variable.
