---
title: "statinterface"
author: "Yaswanth Pulavarthi"
date: "8/25/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stats)
data(ToothGrowth)
library(ggplot2)
library(dplyr)

```
## Load the ToothGrowth data and perform some basic exploratory data analyses

```{r cars}
qplot(dose, len, data = ToothGrowth, color = supp, geom = "point") +  geom_smooth(method = "lm") + labs(title = "ToothGrowth") + labs(x = "Dose of supplements", y = "Length of teeth")
```

## Provide a basic summary of the data.

```{r summary, }
summary(ToothGrowth)
sd(ToothGrowth$len)

```

```{r groupbysummary, }
sumstats <- ToothGrowth %>% group_by(supp,dose) %>% summarize(len.mean=mean(len),)
sumstats
```

## Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)

```{r ttest0.5,}

dose0.5 <- ToothGrowth[ToothGrowth$dose == 0.5, ]
t.test(x = dose0.5$len, paired = FALSE, conf.level = 0.95)$conf.
```


```{r ttest1, }

dose1 <- ToothGrowth[ToothGrowth$dose == 1, ]
t.test(x = dose1$len, paired = FALSE, conf.level = 0.95)$conf.
```

```{r ttest2, }

dose2 <- ToothGrowth[ToothGrowth$dose == 2, ]
t.test(x = dose2$len, paired = FALSE, conf.level = 0.95)$conf.
```


## State your conclusions and the assumptions needed for your conclusions.
There is difference between using OJ and VC, when a dose value is 0 and 1.And, OJ is more effective than VC. it's almost same when dose value is 2. And, confidence intervals are overlapped , so it's difficult to say which one is more helpful


